Applied Measure Theory for Probabilistic Modeling

### 2022-05-20 paper/paper.tex
Update paper/paper.tex
Co-authored-by: Moritz Schauer <moritzschauer@web.de>

For spaces that are ``small enough'', a meaningful probability can be assigned to each subset of the space. Unfortunately, this is impossible for any space containing a continuum such as the real line. Just representing a single arbitrary subset of the \verb|Float64|-range, the computational abstraction of the real line, would require staggering 2\,306 Petabytes of memory. This is not practical.

>>>>

For spaces that are ``small enough'', a meaningful probability can be assigned to each subset of the space. 
But even in moderately sized spaces this can become infeasible: Just representing a single arbitrary subset of the \verb|Float64|-range, the computational abstraction of the real line, would require staggering 2\,306 Petabytes of memory. This is not practical. And for any space containing a continuum such as the real line it becomes not impractical but mathematically impossible to assign a meaningful probability to all subsets.
